Twists of supersymmetric gauge theories

### 2019-08-18 paper.tex
Added a proof of rotation invariance of the supertranslation action

The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.  Let $\d^{\mr{rot}}_{\mr{CE}}$ denote the Chevalley Eilenberg differential in the super Lie algebra $\so(n) \ltimes \Pi \Sigma$.  The total Chevalley-Eilenberg differential, applied to a functional $F$ on the purely fermionic part of the super Poincar\'e algebra, is therefore the sum
\[\d_{\mr{CE}}(Q) = \d^\Gamma_{\mr{CE}}(Q) + \d^{\mr{rot}}_{\mr{CE}}(Q).\]

@@

\begin{proof}
If we consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
\chris{...}
\end{proof}

>>>>

The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.  Let $\d^{\mr{rot}}_{\mr{CE}}$ denote the Chevalley Eilenberg differential in the super Lie algebra $\so(n) \ltimes \Pi \Sigma$.  The total Chevalley-Eilenberg differential, applied to a functional $F$ on the purely fermionic part of the super Poincar\'e algebra, is therefore the sum
\[\d_{\mr{CE}}(F) = \d^\Gamma_{\mr{CE}}(F) + \d^{\mr{rot}}_{\mr{CE}}(F).\]

@@

\begin{proof}
Let $X$ be an element of $\so(n)$, and write $X \cdot A$ and $X \cdot \lambda$ for the image of the fields $A$ and $\lambda$ under the action of the symmetry $X$.  In particular, we can write
\[I_{\mr{rot}}(A,\lambda, A^\vee, \lambda^\vee, X) = \langle A^\vee, X \cdot A \rangle + \langle \lambda^\vee, X \cdot \lambda \rangle.
\]
Therefore, the operator $\{I_{\mr{rot}}(X), -\}$ on the space of local functionals is freely generated by the operator on linear functionals in the Yang-Mills BV fields given by the action of the rotation $X$.  On the other hand, the Chevalley-Eilenberg differential $\d^{\mr{rot}}_{\mr{CE}}$ is freely generated by the operator on \emph{supertranslations} in $\Sigma$, sending $Q$ to $X \cdot Q$.

So, for the functionals at hand, we compute
\begin{align*}
\{I_{\mr{rot}}, I^{(1)}\}(A,\lambda, A^\vee, \lambda^\vee, Q, X) &= \<X \cdot A^* , \Gamma(Q, \lambda)\> + \<A^* , \Gamma(Q, X \cdot \lambda)\> + \<X \cdot \lambda^*, \sd F_A Q\> +  \<\lambda^*, \sd F_{X \cdot A} Q\> \\
&= -\big(A^* , X \cdot \Gamma(Q, \lambda)\> - \<A^* , \Gamma(Q, X \cdot \lambda)\>\big) - \big(\<\lambda^*, X \cdot( \sd F_A Q)\> -  \<\lambda^*, \sd F_{X \cdot A} Q\>\big)\\
&= - \<A^* , \Gamma(X \cdot Q, \lambda)\> - \<\lambda^*, \sd F_A (X \cdot Q)\>\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(1)},
\end{align*}
and
\begin{align*}
\{I_{\mr{rot}}, I^{(2)}\}(\lambda^\vee, Q_1, Q_2 X) &= \left\<X \cdot \lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* + \frac 12 \left((Q_2, X \cdot \lambda^*)Q_1 + (Q_1, X \cdot \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; X \cdot(\rho(\Gamma(Q_1,Q_2)) \lambda^*) + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (Q_1, \lambda^*)X \cdot Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* - \frac 12 \left((X \cdot Q_2, \lambda^*)Q_1 - (X \cdot Q_1,  \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; \rho(\Gamma(X \cdot Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (X \cdot Q_1, \lambda^*)Q_2\right)\right\> - (1 \leftrightarrow 2)\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(2)}.
\end{align*}
\chris{I should take care that the signs I introduce when I move $X$ around are all correct here, and probably include more explanation.}
\end{proof}
